Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-01-21 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The proposed synthesis approach was evaluated in seven stand-alone PV system case studies. Here we report each case study as a tuple \textit{\{power peak (W); power surge (W); energy consumption (Wh/day); battery autonomy (hours)\}} as follows:
\textbf{case study 1:} \{342; 342; 3,900; 48\}; \textbf{case study 2:} \{814; 980; 4,880; 48\}; \textbf{case study 3:} \{815; 980; 4,880; 12\}; \textbf{case study 4:} \{253; 722; 3,600; 48\}; \textbf{case study 5:} \{263; 732; 2,500; 48\}; \textbf{case study 6:} \{322; 896; 4,300; 48\}; \textbf{case study 7:} \{1,586; 2,900; 14,000; 48\}.
These case studies were defined based on the usual electrical load found in riverside communities in the State of Amazonas, Brazil~\cite{TrindadeCordeiro19,Agrener2013}, except for case 7, which was idealized as a small-town solution to support a few lamps and a 12k BTUs air-conditioner. For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house. Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.

Three start-of-the-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with the  Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.

@@

Concerning the off-the-shelf simulation tools, only HOMER Pro performs off-grid system with battery backup analysis and includes economical analysis. Here we used HOMER Pro version $3.13.1$ as a state-of-the-art simulation tool for comparison purposes. In particular, HOMER Pro has the following characteristics:

\begin{itemize}
\item It is available only for MS Windows; its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
\item It does not have LCC cost in its reports, only Net Present Cost (NPC); however, we can obtain LCC from NPC; 
\item The optimization analysis of HOMER defines a load curve and temperature according to data collected from online databases. However, to allow a correct comparison, the curve load and the temperature were defined the same as our synthesis approach; 
\item It does not have a charge controller. During the tests, we have chosen the ``load-following'' option, which produces enough power to meet the demand~\cite{HOMER} and (usually) presents a non-overestimated solution; 
\item It was assumed the value of 95\% availability of the PV system. By definition, ``availability'' is the percentage of time at which a power system can feed the load requirements~\cite{Khatib2014}. For ordinary house electrical load, 95\% is considered acceptable;
\item It was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for our automated synthesis tool; 
\item It was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according to HOMER Pro modeling). During run-time, HOMER decides the size in kW of each module based on feasibility and lower cost.
\end{itemize}

@@

Concerning the verifiers' comparison, CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours. Only case study $7$ led to a \textit{time out} result in CPAchecker. The violation (SAT result) indicated in the on-line table\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}} is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}. CBMC and ESBMC are unable to produce any conclusive results since \textit{time-outs} or \textit{memory-outs} occurred; these results partially answer the \textit{EG1} and \textit{EG2}, because there exist optimal solutions for these case studies and CPAchecker presented the best results among the verifiers.

In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our synthesis approach. To compare the results obtained from the optimization, the authors have four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State, Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, with a configuration of $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries. These deployed systems are closer to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EG1}.

>>>>

The proposed synthesis approach was evaluated in seven stand-alone PV system case studies. Here we report each case study as a tuple \textit{\{power peak (W); power surge (W); energy consumption (Wh/day); battery autonomy (hours)\}} as follows:
\textbf{1:} \{342; 342; 3,900; 48\}; \textbf{2:} \{814; 980; 4,880; 48\}; \textbf{3:} \{815; 980; 4,880; 12\}; \textbf{4:} \{253; 722; 3,600; 48\}; \textbf{5:} \{263; 732; 2,500; 48\}; \textbf{6:} \{322; 896; 4,300; 48\}; \textbf{7:} \{1,586; 2,900; 14,000; 48\}.
These case studies were defined based on the usual electrical load found in riverside communities in the State of Amazonas, Brazil~\cite{TrindadeCordeiro19,Agrener2013}, except for case 7, which was idealized as a small-town solution to support a few lamps and a 12k BTUs air-conditioner. For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house. Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems. 
%
Three start-of-the-art verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} v6.0.0 with the  Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.

@@

Concerning the off-the-shelf simulation tools, only HOMER Pro performs off-grid system with battery backup analysis and includes economical analysis. Here we used HOMER Pro version $3.13.1$ as a state-of-the-art simulation tool for comparison purposes. In particular, HOMER Pro has the following characteristics:
(a) it is available only for MS Windows; its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
(b) it does not have LCC cost in its reports, only Net Present Cost (NPC); however, we can obtain LCC from NPC; 
(c) the optimization analysis defines a load curve and temperature according to data collected from online databases. However, to allow a correct comparison, the curve load and the temperature were defined the same as our synthesis approach; 
(d) it does not have a charge controller. During the tests, we have chosen the ``load-following'' option, which produces enough power to meet the demand~\cite{HOMER} and (usually) presents a non-overestimated solution; 
(e) it was assumed 95\% availability of the PV system. By definition, ``availability'' is the percentage of time at which a power system can feed the load requirements~\cite{Khatib2014}. For an ordinary house electrical load, 95\% is considered acceptable;
(f) it was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for our automated synthesis tool; 
(g) it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW (and with capacity of $83.4$ Ah according to HOMER Pro modeling). During run-time, HOMER decides the size in kW of each module based on feasibility and lower cost.

@@

CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours. Only case study $7$ led to a \textit{time out} result in CPAchecker. The violation (SAT result) indicated in the on-line table\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}} is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}. CBMC and ESBMC are unable to produce any conclusive results since \textit{time-outs} or \textit{memory-outs} occurred; these results partially answer the \textit{EG1} and \textit{EG2}, because there exist optimal solutions for these case studies and CPAchecker presented the best results among the verifiers.

The size of the PV panels and battery bank were larger in HOMER Pro than with our approach. To compare the results obtained from the optimization, the authors have four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State, Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, with a configuration of $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries. These deployed systems are closer to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EG1}.
